\chapter*{Declaration on publications}

This dissertation includes the following articles that have been published in international peer-reviewed journals.

\vspace{20pt}

\textbf{Chapter \ref{ch:roughness} - P. Wechsuwanmanee}, J. Lian, F. Shen, and S. Münstermann, Influence of Surface Roughness on Cold Formability in Bending Processes: A Multiscale Modelling Approach with the Hybrid Damage Mechanics Model, International Journal of Material Forming 14 (2020), 235-248.

\vspace{5pt}

\noindent \url{https://doi.org/10.1007/s12289-020-01576-7}.

\vspace{20pt}

\textbf{Chapter \ref{ch:bending} - P. Wechsuwanmanee}, J. Lian, W. Liu, and S. Münstermann, Numerical Evaluation of Surface Roughness Influences on Cold Formability of Dual-Phase Steel, Steel Research International 91 (2020) 202000141.

\vspace{5pt}

\noindent \url{https://doi.org/10.1002/srin.202000141}.

\vspace{20pt}

\textbf{Chapter \ref{ch:het} - P. Wechsuwanmanee}, J. Lian, S. Münstermann, 3D Multilevel Modeling of Surface Roughness Influences on Hole Expansion Ratios, Steel Research International 92 (2021) 202100449.

\vspace{5pt}

\noindent \url{https://doi.org/10.1002/srin.202100449}

\vspace{20pt}

For the articles published in international journals in Chapter II - Chapter IV, the data curating, numerical model development, and parameter calibration have been performed by the candidate. The preparation of the original draft, including texts, figures and tables, has been provided by the candidate, who has also made the corresponding modifications and improvements in the papers following the suggestions provided by the reviewers.
% % source: https://www.elsevier.com/about/policies/publishing-ethics
In addition, AI-assisted technologies, specifically the OpenAI GPT-4 language model, is employed in this dissertation to improve the readability and language quality. The AI technology was employed exclusively for the purpose of enhancing text readability and language. It was not used to generate data, produce scientific insights, analyze data, draw conclusions, or perform other key actions. The candidate has exercised human supervision in reviewing and refining the content produced by the AI language model.