\chapter*{Curriculum Vitae}\label{ch:cv}
\addcontentsline{toc}{chapter}{Curriculum Vitae} % Add chapter to table of contents
\stepcounter{chapter} % Increase chapter counter

\Large
\textbf{\authorname}

% % Personal information

\normalsize
\begin{tabular}{l  l}
    \textbf{Date of birth:} & 07.01.1988\\
    \textbf{Place of birth:} & \fromcityname \\
    \textbf{Nationality:} & Thai/German \\
    \textbf{E-mail:} & peerapon.wechsuwanmanee@rwth-aachen.de
\end{tabular}

\titlespacing*{\subsection}{0pt}{1.0\baselineskip}{0.2\baselineskip}


% % Education
\subsection*{Education}
\hrule
\vspace*{0.1cm}
\begin{tabular}{l l}
    
    2011 - 2013 & \textbf{M.Sc.} in Computer Aided Conception and Production in Mechanical Engineering,\\
    \hspace*{2.5cm}            & RWTH Aachen University, Germany\\
                \\

    2006 - 2010 & \textbf{B.Eng.} in Electrical-Mechanical Manufacturing Engineering \\
                & Kasetsart University, Thailand \\
                \\

    2001 - 2006 & \textbf{High School Diploma}, Mathematics - Science Programme \\
                & Demonstration School of Nakhon Pathom Rajabhat University, Thailand
                
\end{tabular}

% % Professional experience
\subsection*{Professional Experience}
\hrule
\vspace*{0.1cm}
\begin{tabular}{l l}
    
    2022 - Present  & Data/Machine Learning Engineer,\\
    \hspace*{2.5cm}                & Data Reply GmbH, Germany\\
                    \\
    2015 - 2021     & Research Scientist,\\
                    & Steel Institute, RWTH Aachen University, Germany\\
                    \\
    2011 - 2015     & Research Student,\\
                    & Steel Institute, RWTH Aachen University, Germany\\
                    \\
    2014            & Intern Student,\\
                    & Department of Electrical Drive/Electrical System, Robert Bosch GmbH, Germany\\
                    \\  
    2010 - 2011     & University Lecturer,\\
                    & Department of Mechanical Engineering, Kasetsart University, Thailand\\
                    \\
    2009            & Intern Student,\\
                    & Mechanical Engineering Team, MixEn Corporation Co. Ltd., Thailand\\
    
\end{tabular}

% % Publications
\subsection*{Publications}
\hrule
\vspace*{0.2cm}
\begin{itemize}
    \item
    \textbf{P. Wechsuwanmanee}, J. Lian, S. Münstermann, \textbf{``3D Multilevel Modeling of Surface Roughness Influences on Hole Expansion Ratios''}, Steel Research International, 2021. DOI: \url{https://doi.org/10.1002/srin.202100449}
    
    \item
    \textbf{P. Wechsuwanmanee}, J. Lian, F. Shen, S. Münstermann, \textbf{``Influence of surface roughness on cold formability in bending processes: a multiscale modelling approach with the hybrid damage mechanics model''}, International Journal of Material Forming, 2021. DOI: \url{https://doi.org/10.1007/s12289-020-01576-7}
    
    \item
    \textbf{P. Wechsuwanmanee}, J. Lian, W. Liu, S. Münstermann, \textbf{``Numerical Evaluation of Surface Roughness Influences on Cold Formability of DP Steel''}, Steel Research International, 2020. DOI: \url{https://doi.org/10.1002/srin.202000141}
    
    \item
    \textbf{P. Wechsuwanmanee}, W. Zhang, J. Lian, S. Münstermann, \textbf{``A Study of Machine Learning Approaches to Predict Flow Curves at Different Temperatures and Strain-rates''}, The 15th International Conference on Computational Plasticity, 2019. 
    
    \item
    S. Münstermann, \textbf{P. Wechsuwanmanee}, J. Lian, \textbf{``Modelling the surface roughness influence on the hole expansion ratio of multiphase steel''}, IOP Conference Series Materials Science and Engineering, 2019. DOI: \url{https://doi.org/10.1088/1757-899X/651/1/012006}
    
    \item
    S. Münstermann, \textbf{P. Wechsuwanmanee}, J. Lian, S. Münstermann, \textbf{``Scalebridging Approaches to Assess the Edge Crack Sensitivity of Multiphase Steels''}, The 13th International Conference on Numerical Methods in Industrial Forming Processes, 2019.
    
    \item
    S. Münstermann, \textbf{P. Wechsuwanmanee}, W. Liu, J. Lian, \textbf{``Surface roughness influences on localization and damage during forming of DP1000 sheet steel''}, Procedia Manufacturing, 2019. DOI: \url{http://dx.doi.org/10.1016/j.promfg.2019.02.168}
    
    \item
    J. Lian, \textbf{P. Wechsuwanmanee}, W. Liu, J. Lian, \textbf{``A Numerical Approach to Evaluate Roughness Effects on Localization and Damage in Sheet Materials''}, IOP Conference Series Materials Science and Engineering, 2018. DOI: \url{http://dx.doi.org/10.1088/1757-899X/418/1/012038}
    
    \item
    \textbf{P. Wechsuwanmanee}, J. Lian, J. Sukumaran, Á. Kalácska, H. Ben Hamouda, et al., \textbf{``
    Finite Element Model in Abrasion Analysis for Single-Asperity Scratch Test''}, Fracture Fatige and Wear, 2018. DOI: \url{http://dx.doi.org/10.1007/978-981-13-0411-8_68}
    
    \item
    \textbf{P. Wechsuwanmanee}, J. Lian, S. Münstermann, \textbf{``
    Multi-objective Optimization of Multi-scale Finite Element Analysis for Wear Resistant Steel''}, US National Congress on Computational Mechanics, 2017.
    
    \item
    B. Wu, N. Vajragupta, J. Lian, U. Hangen, \textbf{P. Wechsuwanmanee}, S. Münstermann, et al., \textbf{``Prediction of plasticity and damage initiation behaviour of C45E+N steel by micromechanical modelling''}, Materials and Design, 2017. DOI: \url{http://dx.doi.org/10.1016/j.matdes.2017.02.032}
    
    
    \item
    N. Vajragupta, \textbf{P. Wechsuwanmanee}, J. Lian, M. Sharaf, W. Bleck, et al., \textbf{``The modeling scheme to evaluate the influence of microstructure features on microcrack formation of DP-steel: The artificial microstructure model and its application to predict the strain hardening behavior''}, Computational Material Science, 2014. DOI: \url{http://dx.doi.org/10.1016/j.commatsci.2014.04.011}
    
    \item
    K. Sukvichai, \textbf{P. Wechsuwanmanee}, \textbf{``
    Development of the Modified Kinematics for a Wheeled Mobile Robot''}, International Technical Conference on Circuits/Systems, Computers and Communications, 2010.
    
    \item
    S. Thusneyapan, \textbf{P. Wechsuwanmanee}, \textbf{``
    Kinematics Simulation by using MSC.ADAMS for a 6-DOF Industrial Robot Arm''}, Thailand Simulation and Modeling Conference, 2010. 
    
    \item
    J. Srisabye, \textbf{P. Wechsuwanmanee}, Y. Tipsuwan, et al.,\textbf{``Skuba 2008 Team Description''}, 2008.
    
    \end{itemize}